%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {alabs.team} % Organization
    {Almaty, Kazakhstan} % Location
    {Jun. 2020 - current time} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on React, TypeScript, SSR, microfronend, PWA, monorepo, Storybook, Figma.}
        \item {Configuring auto testing (Jest, Enzyme).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {Kolesa Group} % Organization
    {Almaty, Kazakhstan} % Location
    {Jul. 2019 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained market.kz.}
        \item {Launched new ad page redesign for mobile phone browsers, improving contacting for time users and overall.}
        \item {Written unit tests with Jest.}
        \item {Led quick iteration on various UX A/B tests for ad page improving key metrics such as increased number of unique users.}
        \item {Refactored legacy code.}
        \item {Integrated new payment service.}
        \item {Integrated sentry.io to handle and monitoring errors.}
        \item {Created Email templates with foundation-emails-template.}
        \item {Built web apps in webview android and ios.}
        \item {Configured monorepo with Lerna and Yarn Workspace.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {Vue Storefront} % Organization
    {Warsaw, Poland} % Location
    {Nov. 2018 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed open source project}
        \item {Worked on Vue and PWA}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {Prime Source} % Organization
    {Almaty, Kazakhstan} % Location
    {Mar. 2018 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated from monolith to monorepo with Lerna & Yarn workspace.}
        \item {Built frontend for generalized Internet Banking solution for local banks using TypeScript, React.js, Redux, Rx.js, BEM methodology, D3.js.}
        \item {Covered with Unit tests using Jest, Enzyme, Sinon.js, Mocha.}
        \item {Built Module NCALayerConnector. The module is electronic sign.}
        \item {Was inverviewing several candidates.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {FullStack Developer} % Job title
    {Slon.work} % Organization
    {Almaty, Kazakhstan} % Location
    {Jun. 2017 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained different projects as "Dostykplaza", "Forte.bank", "Naturecool", "Allorange", "We Project" and etc.}
        \item {Refactored legacy code.}
        \item {Worked on Bitrix24 CMS, PHP.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {SBS-IT} % Organization
    {Almaty, Kazakhstan} % Location
    {Mar. 2016 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed e-commerce projects.}
        \item {Build user-friendly UI with HTML, CSS, JS, Gulp, LESS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance FullStack Developer} % Job title
    {TBA} % Organization
    {Almaty, Kazakhstan} % Location
    {Feb. 2015 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and maintened e-commerce projects.}
        \item {Designed database schema and built out backend(PHP, MySql).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
